---
title: "Myanmar News Coverage Analysis"
output:
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: yeti
    source_code: https://github.com/SanHtet-Sanpai/Myanmar-News-R-Project
runtime: shiny

---

```{r setup, include=FALSE, cache=TRUE}

library(ggplot2)
library(viridis)
library(plotly)
library(dygraphs)
library(xts)
library(wordcloud2)
library(DT)
library(htmlwidgets)
library(htmltools)
library(flexdashboard)
library(dplyr)

load("news_data.RData")
```


Words
=========================================================================

col1 {.sidebar}
-----------------------------------------------------------------------
Adjust the parameters of the plots on the right here.

```{r Shiny inputs, warning=TRUE}

shiny::sliderInput("max_words", "Number of Top Words", 
            min = 2, max = 35, value = 10)

shiny::sliderInput("max_sources", "Number of Top Sources", 
            min = 2, max = 35, value = 10)

shiny::sliderInput("hm_words", "Number of Top Words for Heatmap", 
            min = 2, max = 35, value = 10)

shiny::sliderInput("hm_sources", "Number of Top Sources for Heatmap",
            min = 2, max = 35, value = 10)

shiny::numericInput("wc_words", "Number of Top Words for Wordcloud", 200,
              min = 2)

```


col2 {.tabset}
-------------------------------------------------------------------------

### Top Words

```{r Top Words, warning=TRUE}


renderPlotly({
  
  ggplotly(ggplot(topwords[1:input$max_words, ], 
                  aes(x = reorder(word, n), y = n)) + 
             geom_col(aes(fill=tf_idf)) +
             coord_flip() +
             theme_minimal()+
             scale_fill_distiller(direction = 1, palette = "Set1")+
             labs(y = "Word", x = "Frequency", fill = "tf idf score")
         )
  
})
```

### Top Sources

```{r Top Sources, warning=TRUE}

renderPlotly({
  
  ggplotly( ggplot(topsources[1:input$max_sources,],aes(n, source)) +
            geom_col(aes(fill=n)) +
            theme_minimal()+
            scale_fill_distiller(direction = 1, palette = "Set1")+
            labs(y = "Source", x = "Number of Articles", 
                 fill = "Number of Articles")
          )
  

})
```


### Heatmap of Top Words and Top Sources

```{r Heatmap, warning=TRUE}


renderPlotly({
  
  heatmap <- heatmap %>% 
    semi_join(topsources[1:input$hm_sources,], by = "source") %>%
    semi_join(topwords[1:input$hm_words,], by = "word") 
  
  ggplotly(ggplot(heatmap, aes(x = source, y = word, fill =n))+
             geom_tile(aes(text = paste("usage frequency:", n))) +
             scale_fill_viridis(discrete = F, option = "D") +
             theme(axis.text.x = element_blank()) +
             labs(y = "Word", x = "Source", fill = NULL),
           tooltip = c("text", "x", "y")
         )
  
})

```


### Wordcloud

```{r wordcloud, warning=TRUE}

renderWordcloud2({
  
  wordcloud2(topwords[1:input$wc_words, ], shape = "pentagon",
             color= "random-dark")
  
})
```

col4 {data-width=40}
-------------------------------------------------------------------------

### Sources

```{r value box sources, warning=TRUE}

renderValueBox({
 valueBox(length(levels(news$source)), icon = "ion-newspaper-outline", 
          color = "#C1C74C")
})


```

### Articles {data-width=40}

```{r value box articles, warning=TRUE}

renderValueBox({
 valueBox(length(news$title), icon = "ion-document-text-outline",
          color = "#4CC790")
})


```

### From {data-width=40}

```{r value box start, warning=TRUE}

renderValueBox({
 valueBox(as.Date(min(news$date)), icon = "ion-calendar-outline", 
          color = "#524CC7")
})

```

### To {data-width=40}

```{r value box end, warning=TRUE}

renderValueBox({
 valueBox(as.Date(max(news$date)), icon = "ion-calendar-outline", 
          color = "#C74C84")
})

```

### Duration in Days {data-width=40}

```{r value box duration, warning=TRUE}

renderValueBox({
 valueBox(as.integer(difftime(max(news$date), min(news$date)), 
                     unit = "day"), 
          icon = "ion-calendar-clear-outline",
          color = "#C7904C"
          )
})

```

Sentiments(Scaled)
=========================================================================

col1 {.tabset}
-------------------------------------------------------------------------

### Avgerage sentiment by source

```{r avg sent source, warning=TRUE}


renderPlotly({
  

  ggplotly(ggplot(avg_sent, aes(Source, Sentiment, 
                                               fill = Lexicon)) +
            geom_col(show.legend = FALSE) +
            scale_fill_manual(values=c("#C1C74C", "#4CC7C7", "#4C6CC7"))+
            facet_wrap(~Lexicon, ncol = 1, scales = "free_y") +
            ggtitle("Average Sentiment by News Source") +
            theme_minimal()+
            theme(axis.text.x=element_blank(),
                  axis.ticks.x=element_blank()) +
            labs(y = "Sentiment Score", x = "Source", fill = "Lexicon")
  )      
  
})
  
  

```

### Average daily sentiment over Time

```{r daily sent timeline, warning=TRUE}


renderDygraph({
  

  dygraph(time_sent, main= "Average Daily Sentiment over Time")%>%
        dyRangeSelector() %>% 
        dyOptions(stepPlot = TRUE ,colors = c("#C1C74C", "#4CC7C7",
                                              "#4C6CC7"))   %>% 
        dyHighlight(highlightSeriesOpts = list(strokeWidth = 3)) %>% 
        dyEvent("2021-2-2", "Coup", labelLoc = "bottom") %>%
        dyLimit(0, color="red", strokePattern = "solid" )
  
})
  
  

```

### Number of Daily Articles

```{r Number of Articles, warning=TRUE}

renderDygraph({
  
  dygraph(time_article,  main= "Number of Articles over Time") %>% 
    dyOptions( drawPoints = TRUE, pointSize = 4 ) %>% 
    dyRangeSelector()
  
})

```



Data
=========================================================================

col1 
-------------------------------------------------------------------------
### Data Table

```{r datatable, warning=TRUE}


renderDataTable({
  
  datatable <- news %>% 
    select(title, source, date, intro, link)

  datatable(datatable, filter = 'top',
                options =list(autoWidth = T, pageLength = 5))
  
})

```

About
=========================================================================
**Background**  
Coup d'état staged by the Tatmadaw (Myanmar Military) back in February has jeopardized the young democracy the country was enjoying, and undermined its development as well as the livelihood of its people.

**Approach**  
In this project, ~32000 news articles from various news sources were scrapped from the internet and news titles were analyzed.  The project consists of 3 stages-   
1. Web-scrapping the news  
2. Cleaning and processing data  
3. Visualizing the data in a Dashboard  
  
Some of the packages used in each stage are  
1. rvest, dplyr  
2. readr, dplyr, tidyr, tidytext, xts  
3. ggplot2, plotly, wordcloud2, DT, dygraphs, viridis  

Dashboard was built as Shiny Interactive Dashboard using Flexdashboard package. tidytext package was used instead of other popular textmining packages such as tm since the analysis is only performed on news title and no ML model will be used as well as easier work required to create beautiful visualizations. 

The project is constrained in that only titles of news were analyzed and not the actual news body. This is because it is quite difficult (for me at least) to web-scrap news body from hundreds of news sources, each with their own web layout.

**Qualitative Summary of Analysis**  
Unsurprisingly, some of the most commonly used words in news title were "coup", "military", "protest", etc. reflecting the political turmoil of the country. In addition, the average sentiment of all articles by each news source for the duration of time data were collected were overwhelmingly negative. In fact, the sentiments of news article titles significantly dropped after Feb 1st - the day the coup was staged. 


